\documentclass[a4paper,11pt]{article}
\usepackage{url}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1ex}
\setlength{\itemsep}{0pt}
\pagestyle{empty}
\raggedright
\renewcommand{\theenumi}{\alph{enumi}}
\begin{document}

\centerline{\LARGE\bf UNIB20005 Language and Computation}\vspace{2ex}

\centerline{\large\bf Semantics Worksheet 1}\vspace{4ex}

We have seen how to build syntactic representations, with the help of
grammars and parsers.  The next step is to map these tree structures to
representations of meaning.

This week's workshop lays important groundwork for next week's lectures.
We will cover feature-based grammars and first order logic,
drawing on material from the early parts of chapters 9 and 10
in the textbook.

\begin{enumerate}
\item  
  Please read the subsections of \S 9.1 called \emph{Syntactic Agreement}
  and \emph{Using Attributes and Constraints}, then do exercise \S 9.6 ex.~2.

  Homework: read the subsection of \S 9.3 called \emph{Case and
  Gender in German}, then do exercise \S 9.6 ex.~6.  Note that you should
  omit the hyphens from the input words, e.g. \emph{unas cortinas hermosas}.

\item Read \S 10.1, skimming the details and being sure to grasp
  the core concepts, including: database tables, translation of queries into
  SQL, ``truth in a situation'', consistency, and models.  Discuss these
  concepts with a partner, and ask the tutor about any aspects you do
  not understand.
  The book says: ``we have `hard-wired' an embarrassing amount of detail about
  the database''; what is the issue here?  How adequate is SQL as a
  representation of the meaning of a question?  Explain your understanding
  to the tutor.

\item Read \S 10.2, then complete \S 10.8 ex.~1 (a-c).  Show your work
  to the tutor.

  Homework: finish ex.~1. 

\item Read \S 10.3, then attempt \S 10.8 ex.~2 (a-c), 3 (a-c).

  Homework: finish ex.~2, 3.

\end{enumerate}

Please complete the homework tasks before the semantics lectures, where
knowledge of this material will be assumed.
If you have difficulties outside the workshop, please post questions on Discussion Forum.

\end{document}

